Model LF

### 2022-10-06 max_dp endogen stød.Rmd
commit

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> wage_gap1 > max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> wage_gap1 <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

COMMENT> 
IDENTITY> wage_gap
EQ> wage_gap = (wage_ds_t - max_dp)/max_dp

COMMENT> 
IDENTITY> wage_gap1
EQ> wage_gap1 = (wage_ds_t*(1+inflation) - max_dp)/(wage_ds_t*(1 + inflation))

@@

sens1_00 = S_model$simulation$sens1

@@

@@

yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds

@@

plot(kont_h_ratio_01b, col= "red"); lines(kont_h_ratio_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

```{r}
shock_wage_ds_model_shock=shock_wage_ds_model %>% window(start= c(2016,1))
```

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2016,1),  FREQ='Q')

@@

net_export_05 = xk_ds_05 - mk_ds_05
```

@@

>>>>

COMMENT> 
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> SD1 >=1 & shock_wage_ds_model <= 0
IDENTITY> wage_ds_t
EQ> wage_ds_t= wage_ds*(1+inflation_t) 
IF> TSLAG(wage_gap1,1) > max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= max_dp/(1-max_gap)
IF> TSLAG(wage_gap1,1) <= max_gap & SD1 >=1 & shock_wage_ds_model > 0 
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD2 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD3 >= 1
IDENTITY> wage_ds_t
EQ> wage_ds_t= TSLAG(wage_ds_t,1)
IF> SD4 >= 1

COMMENT> 
IDENTITY> wage_gap
EQ> wage_gap = (wage_ds_t - max_dp)/wage_ds_t

COMMENT> 
IDENTITY> wage_gap1
EQ> wage_gap1 = (wage_ds_t*(1+inflation) - max_dp)/(wage_ds_t*(1+inflation))

@@

wage_gap_00 = S_model$simulation$wage_gap

@@

net_balance_00= xk_ds_00 - mk_ds_00
```

@@

yd_hk_ds_01b = Shock_1b$simulation$yd_hk_ds
wage_gap1_01b = Shock_1b$simulation$wage_gap1
wage_gap_01b = Shock_1b$simulation$wage_gap

@@

plot(kont_h_ratio_01b, col= "red"); lines(kont_h_ratio_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap_01b, col= "red"); lines(wage_gap_00, col = "blue"); 
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()
```

@@

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

wage_gap_05 = Shock_5$simulation$wage_gap
max_gap_05 = Shock_5$simulation$max_gap

inflation_05 = Shock_5$simulation$inflation

net_balance_05= xk_ds_05 - mk_ds_05

@@

plot(wage_gap1_05, col= "red"); lines(wage_gap1_01b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(wage_gap_05, col= "red"); lines(wage_gap_01b, col = "blue");
legend("top",legend=c("Baseline", "Scenario 1"),lty=c(1,1),lwd=c(2),bty="n", col = c("blue", "red")); 
grid()

plot(((wage_ds_05 - wage_ds_00) / wage_ds_00), col= "black", xlab= "Year", ylab= "% Change in wage", main= "Wage");
grid()

plot((wage_gap1_05), col= "black", xlab= "Year", ylab= "% Change in compensation rate", main= "compensation rate");
grid()
```

plot(((pconk_ds_05 - pconk_ds_00) / pconk_ds_00), col= "black", xlab= "Year", ylab= "% Change in consumption", main= "Consumption");
grid()

plot(((ik_05 - ik_00) / ik_00), col= "black", xlab= "Year", ylab= "% Change in investments", main= "Investment");
grid()
```

plot(((net_balance_05 - net_balance_00) / net_balance_00), col= "black", xlab= "Year", ylab= "% Change in net balance", main= "Net balance");
grid()

plot(((u_ds_05 - u_ds_00) / u_ds_00), col= "black", xlab= "Year", ylab= "% Change in employment", main= "");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

plot(((yk_ds_05 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((emp_05 - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```
